### 2010-09-25 trunk/paper/IIWAS2010/content/related_work.tex
final after working with Pete

Several other QA systems that use the web as a resource have been developed. Example systems are START\footnote{start.csail.mit.edu} and Swingly\footnote{swingly.com}.  These systems use web pages from searches web crawlers or search engines to find answers.  Morpheus differs in that it seeks out relevant deep web sources, and instead of using a web search engine, it uses only the pages referenced in a previously answered question.

@@

We use YAGO's principles to construct ontologies that provide similarity measures for answering questions within the same domain.  Thus far, these ontologies can be used to classify terms, however their classes do not always appropriately categorize query parameters.  It is necessary to provide an appropriate level of class granularity.  Therefore, we are investigating  methods of identifying classes and their instances from deep web forms and documents.

>>>>

Several other QA systems that use the web as a resource have been developed. Example systems include START\footnote{http://start.csail.mit.edu} and Swingly\footnote{http://swingly.com}.  These systems use web pages from searches web crawlers or search engines to find answers.  Morpheus differs in that it seeks out relevant deep web sources, and instead of using a web search engine, it uses only the pages referenced in a previously answered question.

@@

We use YAGO's principles to construct ontologies that provide similarity measures for answering questions within the same domain.  Thus far, these ontologies can be used to classify terms, however their classes do not always appropriately categorize query parameters.  It is necessary to provide an appropriate level of class granularity.  Section \ref{sec:systemarch} discusses our approach for identifying classes and their instances from deep web forms and documents.
